Classless Java: Tuning Java Interfaces

### 2015-11-30 paper/sections/CaseStudy.tex
code for expression problem updated.

\paragraph{Initial System}
In the formulation of the EP there is an initial system that models
arithmetic expressions with only literals and addition, and an initial 
operation:

\begin{lstlisting}[multicols=2]
interface Exp { int eval(); }

@Obj interface Lit extends Exp {
	int x();
	default int eval() { return x(); }
}
@Obj interface Add extends Exp {
	Exp e1(); Exp e2();
	default int eval() {
		return e1().eval() + e2().eval();
	}
}
\end{lstlisting}

% \begin{multicols}{2}
% \lstinputlisting[linerange=34-44]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_INIT
% \end{multicols}

\noindent \texttt{Exp} is the common super-interface with an evaluation operation
\texttt{eval()} inside. Sub-interfaces \texttt{Lit} and \texttt{Add} extend
interface \texttt{Exp} with default implementations for the \texttt{eval}
operation. The number field \texttt{x} of a literal is represented as a getter
method \texttt{x()} and expression fields (\texttt{e1} and \texttt{e2}) of an addition as
getter methods \texttt{e1()} and \texttt{e2()}.

@@

\marco{text under need to be improved}
\paragraph{Adding a New Operation} The difficulty of the EP in object-oriented 
languages arises from adding new operations. For example, adding a pretty printing 
operation, would typically involve changing all of the existing code. However, a solution 
to the EP forbids this and it also forbids using casts. In other words, it should be possible 
to add the pretty printing operation in a type-safe and modular way.  
It turns out that, this can be done easily, using our object interfaces approach. 
The following code shows how to add the new operation \texttt{print}.

\marco{ use the twoc colums here too}
\lstinputlisting[linerange=53-61]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_PRINT
%\bruno{Please add a Java comment to the code emphasizing that the types of the getters are refined!}
%\bruno{please indent code properly (the getters are not aligned with default))}

>>>>

\paragraph{Initial System}
\yanlin{code figure updated.}
In the formulation of the EP there is an initial system that models
arithmetic expressions with only literals and addition, and an initial 
operation \texttt{eval} for expression evaluation.

\noindent As shown in Figure~\ref{fig:ep}, \texttt{Exp} is the common
super-interface with an evaluation operation \texttt{eval()}
inside. Sub-interfaces \texttt{Lit} and \texttt{Add} extend interface
\texttt{Exp} with default implementations for the \texttt{eval} operation. The
number field \texttt{x} of a literal is represented as a getter method
\texttt{x()} and expression fields (\texttt{e1} and \texttt{e2}) of an addition
as getter methods \texttt{e1()} and \texttt{e2()}.

\begin{figure}
\begin{tabular}{l|l}
\begin{minipage}{8cm}
%\vspace{-90pt}
\begin{lstlisting}[]
interface Exp { int eval(); }
@Obj interface Lit extends Exp {
	int x();
	default int eval() { return x(); }
}
@Obj interface Add extends Exp {
	Exp e1(); Exp e2();
	default int eval() {
		return e1().eval() + e2().eval();
	}
}
\end{lstlisting}
\end{minipage}
&
\begin{minipage}{8cm}
\lstinputlisting[linerange=53-61]{../UseMixinLombok/src/test/TestExpression.java}% APPLY:linerange=EXPRESSION_PRINT
\end{minipage}
\end{tabular}
\caption{The Expression Problem. Initial system on the left, and code for adding
  print operation on the right. }\label{fig:ep}
\end{figure}

@@

\marco{text under need to be improved}
\paragraph{Adding a New Operation} The difficulty of the EP in object-oriented 
languages arises from adding new operations. For example, adding a pretty printing 
operation, would typically involve changing all of the existing code. However, a solution 
to the EP forbids this and it also forbids using casts. In other words, it should be possible 
to add the pretty printing operation in a type-safe and modular way.  
It turns out that, this can be done easily, using our object interfaces approach. 
The code in Figure~\ref{fig:ep} shows how to add the new operation \texttt{print}.
